Heterogeneity in pregregistered multi-lab studies

### 2018-03-16 code/heterogeneity.rmd
Fixed incorrect conditional for countries for ml3
Heterogeneity table also updated to be more consistent

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
```

@@

    fit <- fit2 <- rma(measure = "COR", ri = effect_size, ni = Ntotal, test = "knha", data = x)

    I2_1 <- confint(fit2)$random[3, ]
    I2_2 <- rep(NA, 3)
    #In this case, stop function and return dataframe below
    return(data.frame(s_I2 = I2_1[1], s_ci.lb = I2_1[2], s_ci.ub = I2_1[3], r_I2 = I2_2[1], r_ci.lb = I2_2[2], r_ci.ub = I2_2[3])) #output is for smd, r, and 1 raw difference

@@

    fit <- rma(measure = "OR2D", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2, #standardized
               n1i = ntreatment, n2i = ncontrol, test = "knha", data = x)

@@

res <- dat %>% 
  filter(!rs == "RRR5") %>% #Remove RRR5 for now because have not been able to extract sufficient data for it
  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
  map_dfr(est_heterogen_smd_raw, .id = "effect") %>% #apply function, rbind results into dataframe ('dfr'), 
  mutate(dif = s_I2 - r_I2) #Gives us the difference between the two

#Add rs to the data-frame
het <- dat %>% 
  select(rs, effect) %>% 
  group_by(rs, effect) %>% 
  summarize() %>% 
  left_join(res) %>% 
  arrange(rs, desc(s_I2)) #sort by rs and I2 for standardized effect

@@

```{r table}
library(kableExtra)
het %>% knitr::kable("latex", booktabs = T, digits = 1, col.names = c("RS", "Effect", "I2(%)", "ci.lb", "ci.ub", "I2(%)", "ci.lb", "ci.ub", "Dif")) %>% 
  kable_styling() %>% 
  add_header_above(c(" " = 2, "Standardized" = 3, "Unstandardized" = 3, " " = 1))

```
**Note**: I am uncertain if we can speak of standardized/unstandardized in regards to 2x2 tables? For now these correspond to OR/Risk difference for the following five effects {Allowed vs forbidden, gain vs. loss framing, norm of reciprocity, low vs. high category scale, verbal overshadowing}. NA in unstandardized columns comes from correlations which don't seem possible to calculate the unstandardized version for with the available information. RRR5 I have not yet been able to extract a measure of variance for, hence the NAs.

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

@@

    fit <-rma(measure = "ZCOR", ri = effect_size, ni = Ntotal, test = "knha", data = x) #Fisher's r-to-z transformed correlation coefficient
    fit2 <- rma(measure = "COR", ri = effect_size, ni = Ntotal, test = "knha", data = x) #raw correlation

@@

    fit <- rma(measure = "OR2DL", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2, #standardized, ML1 used 'OR2D' but this = 'OR2DL'
               n1i = ntreatment, n2i = ncontrol, test = "knha", data = x)

@@

#--------------
res <- dat %>% 
  filter(!rs == "RRR5") %>% #Remove RRR5 for now because have not been able to extract sufficient data for it
  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
  map_dfr(est_heterogen_smd_raw, .id = "effect") %>% #apply function, rbind results into dataframe ('dfr'), make sure purrr is up to date
  mutate(dif = s_I2 - r_I2) #Gives us the difference between the two

clarify <- c("Allowed vs. forbidden", "Gain vs. loss framing", "Norm of reciprocity", "Low vs. high category scales")

#-----------TEST
test <- dat %>% filter(effect == "IAT correlation math")
fit <- rma(measure = "ZCOR", ri = effect_size, ni = Ntotal, test = "knha", data = test)
fit2 <- rma(measure = "COR", ri = effect_size, ni = Ntotal, test = "knha", data = test)

#---------
#Add rs to the data-frame
het <- dat %>% 
  select(rs, effect, effect_type) %>% 
  group_by(rs, effect) %>% 
  summarize(effect_type = unique(effect_type)) %>% 
  left_join(res) %>% 
  mutate(effect_type = recode(effect_type, 
                              d = "Mean diff.",
                              r = "Correlation",
                              'Raw mean difference' = "Mean diff.",
                              'Risk difference' = "OR / RD"),
         effect_type = ifelse(effect %in% clarify, "OR / RD", effect_type)) %>% 
  arrange(desc(s_I2)) #sort by rs and I2 for standardized effect

@@

```{r table}
library(kableExtra)
het %>% knitr::kable("latex", booktabs = T, digits = 1, col.names = c("RS", "Effect", "Effect type", "I2(%)", "ci.lb", "ci.ub", "I2(%)", "ci.lb", "ci.ub", "Dif")) %>% 
  kable_styling() %>% 
  add_header_above(c(" " = 3, "Standardized" = 3, "Unstandardized" = 3, " " = 1))

```
**Note**: "OR / RD" indicates that the effect was meta-analyzed as odds ratio in 'standardized' columns and risk difference in 'unstandardized' columns. Out of these effects 'Verbal overshadowing' was meta-analyzed by original authors as risk difference and the others as odds ratios. For correlations the standardized version correspond to Fisher's r-to-z transformed correlation and unstandardized to raw correlations. All original authors used raw correlations in their meta-analyzes. For 'Mean diff.' the standardized version corresponds to Hedge's g and unstandardized to raw mean differences. Original authors used different approaches for mean differences. RRR5 I have not yet been able to extract a measure of variance for, hence the NAs. Effects were estimated in metafor using REML with the "knha" correction.

For RRR8 the analysis includes data from all 40 laboratories, the preregistered RRR8 analysis only included 23 laboratories (the rest didn't collect enough male participants) - needs fixing.
